Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-06-08 Manuscript/MPESubmission/TEM_draft.tex
Initial commit of cover letter for MPE

\subsection*{Data reproducibility and availability}
\noindent{\bf Data reproducibility and availability.} All the code used in this analysis is available on \href{https://github.com/TGuillerme/Total_Evidence_Method-Missing_data}{\color{blue}{GitHub}} with some information on how to use the various functions. Additionally all the simulated data is available on \href{http://figshare.com/articles/Effect_of_missing_data_on_topological_inference_using_a_total_evidence_approach/1306861}{\color{blue}{FigShare}}.

>>>>

\subsection*{Data reproducibility and availability}
\noindent{\bf Data reproducibility and availability.} All the code used in this analysis is available on \href{https://github.com/TGuillerme/Total_Evidence_Method-Missing_data}{\color{blue}{GitHub}} (\href{https://github.com/TGuillerme/Total_Evidence_Method-Missing_data}{    
goo.gl/4djNUf}) with some information on how to use the various functions. Additionally all the simulated data is available on \href{http://figshare.com/articles/Effect_of_missing_data_on_topological_inference_using_a_total_evidence_approach/1306861}{\color{blue}{FigShare}} (dx.doi.org/10.6084/m9.figshare.1306861).
